
\documentclass{article}
\usepackage[utf8]{inputenc}  
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}  % Multi-page tables
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{multirow}  % Allows merging cells
\usepackage{xcolor}
\begin{document}

\section*{Circuit Analysis Examples}

\noindent Below is a unified table of all circuits.

\small
\begin{longtable}{|p{0.15\textwidth}|p{0.45\textwidth}|p{0.35\textwidth}|}
\hline
\textbf{Id ($P_{act}$)} & \textbf{Input Text} & \textbf{Top Logits} \\
\hline
\endfirsthead  % Header repeated on new pages
\hline
\textbf{Id ($P_{act}$)} & \textbf{Input Text} & \textbf{Top Logits} \\
\hline
\endhead

\hline
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\hline
\endfoot

\hline
\endlastfoot
& & \\
\multirow{5}{*}{\textbf{0 (0.072)}} & be more careful when eating spicy food. From that & day, day,  Monday, side, night \\
& too because she helped the bird. From that & day, side, umm, ts,  Balls \\
& she should have been more careful. From that & day, day, side, cers, ts \\
& tummy hurt. From that & day, side,  Balls, acas, ters \\
& . From that & day, side, acas, cers,  Balls \\
& & \\
\multirow{5}{*}{\textbf{1 (0.114)}} & me."  Lily smiles and claps her & hands,  voices,  mouths,  faces, oves \\
& sit next to each & other, other,  their,  our,  ours \\
& time, there was a little boy named Timmy. & Tim,  One,  They,  It,  There \\
& on a camping trip. Timmy was very excited!   As & they,  their,  them, They,  theirs \\
& saw a cat on a tree. He wanted to be & friends,  their,  animals,  our,  together \\
& & \\
\multirow{5}{*}{\textbf{2 (0.036)}} & They are sad. They want to see the treasure. & <|endoftext|>, They, ", The, But \\
& car, a flower and a star. & <|endoftext|>, ", They,  , The \\
& did not know why. & <|endoftext|>, The, ",  , They \\
& and loud. They did not hear their mom calling them. & <|endoftext|>, ",  , They, The \\
& basket and the knife behind. & <|endoftext|>, ",  , They, The \\
& & \\
\multirow{5}{*}{\textbf{3 (0.063)}} & fun day at the park.Once upon a time, there was a boy named & Tim,  Jack,  James,  Lily,  Alex \\
& ."Once upon a time, there was a boy named & Tim,  Jack,  Lily,  Ben,  James \\
& They pretended to be kings and & queens,  she,  princes,  her,  She \\
& in the future.Once upon a time, there was a big elephant named & Ellie,  Ell,  Daisy,  Grace,  Lily \\
& Once upon a time, there was a boy named Tim. & He,  Every,  She,  They,  Sue \\
& & \\
\multirow{5}{*}{\textbf{4 (0.111)}} & , doctor. Thank you, mom. Thank you & ,,  Star, ider,  printers,  Auto \\
& . It looked happy and friendly.  "See, Lily and Ben & ,, ?", !", ?!", !, \\
& panic and cry. Her mom knew it & and, ., ,,  would,  wasn \\
& , Mom. Please, can & we,  I,  pie,  soldiers,  Hood \\
& 't worry, Timmy & ., ,", !, .", !" \\
& & \\
\multirow{5}{*}{\textbf{5 (0.107)}} & together.Once upon & a,  an, SEC, irled, clip \\
& best friends.Once upon & a,  an, SEC, clip, irled \\
& , so they stay colorful and clean."Once upon & a,  an, orse, ship, ream \\
& you for being so persistent, daddy."Once upon & a,  an, ud, orse, SEC \\
& became good friends.Once upon & a,  an, clip, SEC, irled \\
& & \\
\multirow{5}{*}{\textbf{6 (0.229)}} & to play. They went on the swings and the slide. Lily had so & much,  killing,  backdrop,  doorstep, ocus \\
& way there, he got lost. He couldn't find his & way,  results, rr, umbers, For \\
& noises. Tom had a small car that could go fast and beep. Lily & wanted,  liked,  was,  loved,  and \\
& teddy bear and had a lot of & fun,  adventure,  lots,  daring,  thrilling \\
& jump in. They had so & much,  satisfying, wr, Ah, izz \\
& & \\
\multirow{5}{*}{\textbf{7 (0.085)}} & They made a new friend. They were very happy & .,  elegance, effective, ulent, val \\
& your dragon."  They all laughed and hugged. They were happy and glad & ., unky, utch, aved,  cog \\
& ice cream. It was cold and sweet. They were very happy & ., iot,  error, angled, uld \\
& They are sad & and, stack, Figure, rast, wered \\
& and milk. Lily was very happy & and, ., redible, ulent,  arise \\
& & \\
\multirow{5}{*}{\textbf{8 (0.067)}} & said to the plant, "We are sorry, plant. We did & not, t,  opposite,  roll, pe \\
& mister," Tom says. "We did & not, t, ts,  still,  steadily \\
& worm," she said. "I'm sorry, mushroom. I did & not, t,  roll, ts,  sly \\
& marks on the wall too, but Mommy does & not, .),  trade,  ll,  fir \\
& The bee was on the apple. It was angry and scared. It did & not,  roll, ves, dig, not \\
& & \\
\multirow{5}{*}{\textbf{9 (0.177)}} & ran to hide behind a tree. She peek & ed, apped, red, faced,  Buddha \\
& it in the lock. They push and pull, but nothing & happened,  comes,  works,  is,  breaks \\
& Mommy will be angry. He says, & ", ulating, ver, attered, atter \\
& you for the treat!" Spot bark & ed, ked, red, apped, led \\
& . Lily pet & ted, ged, led, aced, oled \\

\end{longtable}

\end{document}
